BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-25 tex/1-intro.tex
Minor fixes in captions + some of variations subsection.

Aims and contributions of this work. Example from my last paper to see the format:
\surl{http://purl.pt/24107/1/iPres2013_PDF/CLEAR\%20a\%20credible\%20method\%20to\%20evaluate\%20website\%20archivability.pdf}

>>>>

Aims and contributions of this work. Example from my last paper to see the format:\\
http://purl.pt/24107/1/iPres2013\_PDF/\\
CLEAR\%20a\%20credible\%20method\%20to\%20\\
evaluate\%20website\%20archivability.pdf

### 2013-11-25 tex/2-related-work.tex
Minor fixes in captions + some of variations subsection.

Web Object Identification for Web Automation and Meta-Search,
\surl{http://www.dbai.tuwien.ac.at/proj/tamcrow/download/Kordomatis2013WIMS.pdf}

Self-supervised Automated Wrapper Generation for Weblog Data Extraction,
\surl{https://github.com/OlivierBlanvillain/blogforever-crawler-publication/raw/master/papers/bncod_published.pdf}

Web Data Extraction, Applications and Techniques: A Survey,
\surl{http://www.emilio.ferrara.name/wp-content/uploads/2011/07/survey-csur.pdf}

Archiving Data Objects using Web Feeds,
\surl{http://hal.archives-ouvertes.fr/docs/00/53/79/62/PDF/iwawienna.pdf}

Intelligent and Adaptive Crawling of Web Applications for Web Archiving,
\surl{http://pierre.senellart.com/publications/faheem2013intelligent.pdf}

Zero-cost Labelling with Web Feeds for Weblog Data Extraction,
\surl{http://www2013.org/companion/p73.pdf}

OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications,
\surl{http://www.vldb.org/pvldb/vol4/p1016-furche.pdf}

>>>>

Web Object Identification for Web Automation and Meta-Search,
\\
http://www.dbai.tuwien.ac.at/proj/ta\\
mcrow/download/Kordomatis2013WIMS.pdf

Self-supervised Automated Wrapper Generation for Weblog Data Extraction,
\\
https://github.com/OlivierBlanvillai\\
n/blogforever-crawler-publication/raw\\
/master/papers/bncod\_published.pdf

Web Data Extraction, Applications and Techniques: A Survey,
\\
http://www.emilio.ferrara.name/wp-co\\
ntent/uploads/2011/07/survey-csur.pdf

Archiving Data Objects using Web Feeds,
\\
http://hal.archives-ouvertes.fr/docs\\
/00/53/79/62/PDF/iwawienna.pdf

Intelligent and Adaptive Crawling of Web Applications for Web Archiving,
\\
http://pierre.senellart.com/publicat\\
ions/faheem2013intelligent.pdf

Zero-cost Labelling with Web Feeds for Weblog Data Extraction,
\\
http://www2013.org/companion/p73.pdf\\

OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications,
\\
http://www.vldb.org/pvldb/vol4/p1016\\
-furche.pdf

### 2013-11-25 tex/3-algorithms.tex
Minor
Minor fixes in captions + some of variations subsection.

Properties \ref{wordorderProp} and \ref{substringProp} are essential to deal with cases where web feeds contain only an abstract or a subset of the post content. The following table \comment{or with a caption?}illustrates these two properties with examples, also giving the Levenshtein\cite{levenshtein1966} similarity to illustrate poor performances of string matching based similarities.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time complexity and linear reformulation}

% algo 1 is quadratic
With both \coderef{allrulesAlgo} and \coderef{similarityAlgo} function defined, we will now show that Algorithm \ref{extractionAlgo} has a quadratic running time. Let's first assume that we have at our disposal a linear time HTML parser and a data-structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before, the outer loop splits the input into independent computations, and each call to \coderef{allrulesAlgo} returns (in linear time) less rules than the number of nodes of the HTML tree argument. Therefore, the body of the inner loop will be executed a linear number of time. Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for comments, dates and authors}
- comments
- date authors

>>>>

Properties \ref{wordorderProp} and \ref{substringProp} are essential to deal with cases where web feeds contain only an abstract or a subset of the post content. Table \ref{similarityTable} illustrates these two properties with examples, also giving the Levenshtein\cite{levenshtein1966} similarity to illustrate poor performances of string matching based similarities.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time complexity and linear reformulation}
% algo 1 is quadratic
With both \coderef{allrulesAlgo} and \coderef{similarityAlgo} function defined, we will now show that Algorithm \ref{extractionAlgo} has a quadratic running time. Let's first assume that we have at our disposal a linear time HTML parser and a data-structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before, the outer loop splits the input into independent computations, and each call to \coderef{allrulesAlgo} returns (in linear time) less rules than the number of nodes of the HTML tree argument. Therefore, the body of the inner loop will be executed a linear number of time. Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for authors, dates and comments}
% Intro, authors
As is, algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performed poorly for authors and dates extraction and are not suitable for comment extraction. The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score. The heuristic we use to get around this issue consists in adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new score component takes advantage of the positioning of post's authors which is often a direct child or shares parent with the post content node.

% Dates, authors
Dates are affected by the same issue of often being duplicated in a page, which is complexified by the inconsistances of format between the dates provided in web feeds and their representation on web pages. Our solution uses the same tree distance score component presented

% Comments

### 2013-11-25 tex/5-evaluation.tex
Progress...
Progress
Minor fixes in captions + some of variations subsection.

\subsection{Content extraction}
Compare:
\begin{itemize}
  \item Our solution
  \item Boilerpipe q\surl{https://github.com/misja/python-boilerpipe}
  \item Goose \surl{https://github.com/grangier/python-goose}
  \item Readability \surl{https://github.com/buriy/python-readability}
\end{itemize}
On:
\begin{enumerate}
  \item Running time
  \begin{itemize}
    \item Plot duration as a function of the page length
    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
  \end{itemize}
  \item Quality of output compared:
  \begin{itemize}
    \item Chart of success pourcentages
  \end{itemize}
\end{enumerate}

\subsection{JavaScript rendering}
Compare:
\begin{itemize}
  \item "Wget crawl" \surl{http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/}
  \item wkhtmltopdf \surl{http://code.google.com/p/wkhtmltopdf/}
  \item Selenium + full browser
  \item probably others
\end{itemize}
On:
\begin{itemize}
  \item Table comparing functionalities of each solution
  \item Histogram of redering time per browser (phantomjs/chrome/firefox)
\end{itemize}

>>>>

\subsection{Content extraction}
Compare:
\begin{itemize}
  \item Our solution
  \item Boilerpipe https://github.com/misja/python-boilerpipe
  \item Goose https://github.com/grangier/python-goose
  \item Readability https://github.com/buriy/python-readability
\end{itemize}
On:
\begin{enumerate}
  \item Running time
  \begin{itemize}
    \item Plot duration as a function of the page length
    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
  \end{itemize}
  \item Quality of output compared:
  \begin{itemize}
    \item Chart of success pourcentages
  \end{itemize}
\end{enumerate}

\subsection{JavaScript rendering}
Compare:
\begin{itemize}
  \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/\\creating-a-snapshot-of-a-blog-post-using-wget/
  \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/
  \item Selenium + full browser
  \item probably others
\end{itemize}
On:
\begin{itemize}
  \item Table comparing functionalities of each solution
  \item Histogram of redering time per browser\\(phantomjs/chrome/firefox)
\end{itemize}

- ez of use vs power, fine because it's automated
- c++ vs java vs scala vs go \cite{hundt2011}
